\section*{LỜI CẢM ƠN}

Các tác giả xin gửi lời cảm ơn đến Kho lưu trữ Học máy UCI vì đã cung cấp
tập dữ liệu Tiêu thụ Điện năng Ngành thép.
Nghiên cứu này được hỗ trợ bởi [nguồn tài trợ nếu có].

% =============================================================================
% TÀI LIỆU THAM KHẢO
% =============================================================================
\begin{thebibliography}{00}

\bibitem{hippert2001}
H.~S. Hippert, C.~E. Pedreira, and R.~C. Souza, ``Neural networks
for short-term load forecasting: A review and evaluation,''
\emph{IEEE Trans. Power Syst.}, vol.~16, no.~1, pp. 44--55,
Feb. 2001.

\bibitem{bouktif2020}
S.~Bouktif \emph{et al.}, ``Optimal deep learning LSTM model for
electric load forecasting using feature selection and genetic
algorithm,''
\emph{IEEE Access}, vol.~8, pp. 152,431--152,445, 2020.

\bibitem{khuntia2016}
S.~R. Khuntia, J.~L. Rueda, and M.~A.~M.~M. van der Meijden,
``Forecasting the load of electrical power systems in mid- and
long-term horizons: A review,''
\emph{IET Gener. Transm. Distrib.},
vol.~10, no.~16, pp. 3971--3977, 2016.

\bibitem{amjady2011}
N.~Amjady and F.~Keynia, ``A new neural network approach to
short term load forecasting of electrical power systems,''
\emph{Energies}, vol.~4, no.~3, pp. 488--503, 2011,
doi: 10.3390/en4030488.

\bibitem{sobhani2019weather}
M.~Sobhani, A.~Campbell, S.~Sangamwar, C.~Li, and T.~Hong,
``Combining weather stations for electric load forecasting,''
\emph{Energies}, vol.~12, no.~8, p. 1510, 2019,
doi: 10.3390/en12081510.

\bibitem{gekeler2025weather}
D.~Gekeler, L.~Baur, F.~Schnell, P.~Hennig, and A.~Sauer,
``Benefit of weather integration for industrial electric load
forecasting---A benchmark study,'' in \emph{Proc. 6th Int.
Conf. Clean and Green Energy Engineering (CGEE)}, 2025,
pp. 84--88, doi: 10.1109/CGEE65971.2025.11327705.

\bibitem{haq2023stacking}
H.~Mubarak, M.~J. Sanjari, S.~Stegen, and A.~Abdellatif,
``Improved active and reactive energy forecasting using a stacking
ensemble approach: Steel industry case study,''
\emph{Energies}, vol.~16, no.~21, p.~7252, 2023,
doi: 10.3390/en16217252.

\bibitem{garcianieto2025interpretable}
P.~J. Garcia-Nieto, E.~Garcia-Gonzalo, L.~A. Menendez-Garcia,
L.~Alvarez-de-Prado, M.~Menendez-Fernandez, and A.~Bernardo-Sanchez,
``Interpretable machine learning models for estimating electric energy
consumption in steel industries,''
\emph{Mathematics}, vol.~13, no.~21, p.~3364, 2025.

\bibitem{openmeteo2026}
Open-Meteo, ``Historical Weather API,'' 2026. [Online].
Available: https://open-meteo.com/en/docs/historical-weather-api

\bibitem{hoffmann2020switchgear}
M.~W. Hoffmann \emph{et al.}, ``Integration of novel sensors and
machine learning for predictive maintenance in medium voltage switchgear
to enable the energy and mobility revolutions,''
\emph{Sensors}, vol.~20, no.~7, p. 2099, Apr. 2020,
doi: 10.3390/s20072099.

\bibitem{batra2014nilmtk}
N.~Batra \emph{et al.}, ``NILMTK: An open source toolkit for
non-intrusive load monitoring,'' in \emph{Proc. 5th ACM Int. Conf.
Future Energy Systems}, 2014, pp. 265--276,
doi: 10.1145/2602044.2602051.

\bibitem{rashid2019nilm}
H.~Rashid, P.~Singh, V.~Stankovic, and L.~Stankovic, ``Can
non-intrusive load monitoring be used for identifying an appliance's
anomalous behaviour?,'' \emph{Applied Energy}, vol.~238, pp. 796--805,
2019, doi: 10.1016/j.apenergy.2019.01.061.

\bibitem{rubin1976}
D.~B. Rubin, ``Inference and missing data,''
\emph{Biometrika}, vol.~63, no.~3, pp. 581--592, 1976.

\bibitem{uci2023}
``Steel Industry Energy Consumption Dataset,'' UCI Machine
Learning Repository. [Online]. Available:
https://archive.ics.uci.edu/dataset/851/

\bibitem{zhang2024}
N.~Zhang \emph{et al.}, ``Deep learning modeling in electricity
load forecasting,''
\emph{Energy Rep.}, vol.~11, pp. 3544--3556,
2024.

\bibitem{mallat1989}
S.~G. Mallat, ``A theory for multiresolution signal decomposition:
The wavelet representation,''
\emph{IEEE Trans. Pattern Anal.
Mach. Intell.}, vol.~11, no.~7, pp. 674--693, Jul. 1989.

\bibitem{chandola2009}
V.~Chandola, A.~Banerjee, and V.~Kumar, ``Anomaly detection:
A survey,''
\emph{ACM Comput. Surv.}, vol.~41, no.~3, pp. 1--58,
2009.

\bibitem{himeur2021review}
Y.~Himeur, K.~Ghanem, A.~Alsalemi, F.~Bensaali, and A.~Amira,
``Artificial intelligence based anomaly detection of energy consumption
in buildings: A review, current trends and new perspectives,''
\emph{Applied Energy}, vol.~287, p.~116601, 2021,
doi: 10.1016/j.apenergy.2021.116601.

\bibitem{zangrando2022quasi}
N.~Zangrando, P.~Fraternali, M.~Petri, N.~O.~P. Vago, and
S.~L.~H. Gonzalez, ``Anomaly detection in quasi-periodic energy
consumption data series: A comparison of algorithms,''
\emph{Energy Informatics}, vol.~5, Suppl.~4, 2022,
doi: 10.1186/s42162-022-00230-7.

\bibitem{ratner2016data}
A.~Ratner, C.~De Sa, S.~Wu, D.~Selsam, and C.~Ré,
``Data programming: Creating large training sets, quickly,''
in \emph{Proc. Advances in Neural Information Processing
Systems (NeurIPS)}, 2016, pp. 3567--3575.

\bibitem{ratner2017snorkel}
A.~Ratner \emph{et al.}, ``Snorkel: Rapid training data creation
with weak supervision,'' \emph{Proc. VLDB Endow.},
vol.~11, no.~3, pp. 269--282, 2017.

\bibitem{goodfellow2014}
I.~J. Goodfellow \emph{et al.}, ``Generative adversarial nets,''
in \emph{Advances in Neural Information Processing Systems
(NeurIPS)}, Montreal, Canada, 2014, pp. 2672--2680.

\bibitem{yoon2019}
J.~Yoon, D.~Jarrett, and M.~van der Schaar, ``Time-series
generative adversarial networks,''
in \emph{Proc. 33rd
Conference on Neural Information Processing Systems (NeurIPS)},
Vancouver, Canada, 2019, pp. 5509--5519.

\bibitem{tang2025}
P.~Tang \emph{et al.}, ``Time series data augmentation for
energy consumption data based on improved TimeGAN,''
\emph{Sensors}, vol.~25, no.~2, p.~493, Jan. 2025.

\bibitem{li2022ttsgan}
X.~Li \emph{et al.}, ``TTS-GAN: A transformer-based time-series
generative adversarial network,''
in \emph{Proc. Artificial Intelligence in Medicine (AIME)},
vol.~1327, 2022, pp. 125--134.

\bibitem{liu2022modwt}
Y.~Liu \emph{et al.}, ``Multiscale analysis of energy time series
using maximal overlap discrete wavelet transform,''
\emph{Energy Econ.}, vol.~109, p. 106, 2022.

\bibitem{abraham2021iso}
A.~Abraham \emph{et al.}, ``CUSUM-based drift monitoring for
ISO~50001 energy performance indicators,''
\emph{Energy Strategy Rev.}, vol.~38, p. 100, 2021.

\bibitem{gebru2021datasheets}
T.~Gebru \emph{et al.}, ``Datasheets for datasets,''
\emph{Commun. ACM}, vol.~64, no.~12, pp. 86--92, Dec. 2021.

\end{thebibliography}
